---
title: "Belt Tension Calculator Presentation"
author: "AntChanCPT"
date: "02/07/2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

This presentation is the second part to the Developing Data Products module on Coursera. As part of the project, a simple shiny application was made and deployed on [shinyapps.io](https://www.shinyapps.io/). 

This application was a calculator which returned the tension of a drive or timing belt (typically of rubber construction) from user input recorded belt frequency and belt properties.

## Equation and Inputs

The equation used for this calculation came from [Pico Technology](https://www.picoauto.com/library/automotive-guided-tests/belt-tension):

T = 4 * m * l^2 * f^2

where T is the belt tension in N,

m is the mass per unit length in kg/m,

l is the length of the belt span in m,

f is the recorded frequency in Hz.

Since mass per unit length is not usually known, this was simply calculated by dividing the mass by the length of the belt.

## Example

The example below uses the default values in the calculator. With a recorded frequency of 200Hz, belt span of 150mm, belt mass of 120g and belt length of 250mm, the belt tension was determined to be 1728N.

```{r example, echo = TRUE}
freq <- 200
span <- 0.150
mass <- 0.120
length <- 0.250

tension <- 4 * (mass / length) * span^2 * freq^2
tension
```

## Links

* The shiny application can be found [here](https://antchancpt.shinyapps.io/CourseProject/).

* The github repo with the ui.R and server.R files can be found [here](https://github.com/AntChanCPT/BeltTensionCalculator).

